Interest Flooding Attacks and Countermeasures in Named Data Networking

### 2013-01-14 05-evaluation.tex
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@921 df1a90cd-247b-4364-bdaf-287a704eb499

\subsection{Limitations}
{\color{red} I gave up the idea of seperate discussion section as after trying for some time, I realized there is no way to write a reasonably comprehensive and acceptably broad discussion section that touches on algorithms, evaluation and methodology, etc. So, I decided to get rid of it and only have a scoped down version here that confesses upon the limiations of our evaluations. Whoever has time, please go ahead and write 1-2 paragraphs as outlined below}

>>>>

\subsection{Limitations}
{\color{red} I gave up the idea of seperate discussion section after trying for some time, as given the space limitation, there is no way to write a reasonably comprehensive and  broad discussion section that justifies a separate section. Instead, I decided to have a scoped down version here that confesses upon the limiations of our evaluations only. Whoever has time (I need to sleep few hours), please go ahead and write 1-2 paragraphs as I outlined below. -Ersin}
